A flexible parallel architecture for\\ high-performance network traffic processing

### 2017-06-11 Paper.tex
2017.6.11

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The abstract goes here.
\end{abstract}

@@

The zero-copy and multi-core technology can help avoid sparse sampling\cite{Ali}.A renowned tool to accomplish zero-copy is PF\_RING\cite{PFRING}.The PF\_RING kernel module runs as a software interrupt handler that stores incoming packets to a memory-mapped buffer,shared with user-level stub.For multi-core technology,there are also various multi-thread proposed methods that can improve the entire performance.

@@

\subsection{PF\_RING Patch}
PF\_RING is a new type of network socket that dramatically improves the packet capture speed.It uses User-space ZC (new generation DNA, Direct NIC Access) drivers for extreme packet capture transmission speed as the NIC NPU (Network Process Unit) is pushing getting packets to user land without any kernel intervention. 
Noff uses PF\_RING as the kernel driver and can thus arrive more aggressive runtime speed.

\subsection{LRU Scheme}
Noff has proposed Least Recently Used(LRU):a stream algorithm which enable the system to control its resources effectively during overload. This algorithm can resolve the problem that sudden traffic bursts or overload conditions may force the packet capturing subsystem to fill up its buffers and randomly drop streams in a haphazard manner.In order to arrive this requirment,noff maintains a novel timer data structure:timing wheel\cite{Varghese}which store the streams into different buckets by the time gap.Timing wheel would drop the streams which have been silent for at least one minute.In this way,the new stream will be accommodated with a higher probability.Besides,Programmers can also force to maintain some priority streams by updating the timestamp of those streams.The detail implementation of timing wheel would be described in the implementation section.

@@

\subsection{Processing Procedure}
Noff uses a multi-layer framework. Each layer is independent and could include a number of modules.A module would offer one or more callback interface for upper layer module to invoke. A stream packet's processing procedure is shown as Figure \ref{fig:3}.
Programmer can add a new module based on one existing layer by themselves.
\begin{figure}
\begin{minipage}[t]{0.495\linewidth}
\flushleft
\includegraphics[width=\textwidth]{./picture/Figure1.jpg}
\caption{Multiqueue capture} 
\label{fig:1}
\end{minipage}
\begin{minipage}[t]{0.495\linewidth}
\flushright
\includegraphics[width=\textwidth]{./picture/Figure2.jpg}
\caption{single queue capture}
\label{fig:2}
\end{minipage}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{./picture/Figure3.jpg}
  \caption{packet processing procedure}
  \label{fig:3}
\end{figure}

@@

    dns.addResponsecallback(bind(
    &UdpClient::onData<DnsResponse>,
    dnsResponseOutput.get(), _1));
}
void initInThread()
{
 setDnsCounterInThread();
}
\end{lstlisting}
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.25\textwidth]{./picture/Figure4.jpg}
  \caption{packet processing procedure}
  \label{fig:4}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.25\textwidth]{./picture/Figure16.jpg}
  \caption{Callback interface scheme}
  \label{fig:5}
\end{figure}
\subsubsection{Memory Optimization}
The TCP reassembly module needs to resort TCP fragments.So it needs to prestore packet data which is meant by a large number of dynamic memory allocation. Libnids not only prestore packets but also store the completed packets between client and server. This scheme has a palpable short slab that there are too many memory allocations and copies which could bring huge overhead.
\newline\indent Basically, noff has abandon the scheme that the reassembly module needs to store the completed packets. Because though libnids offer this ability. The upper applications also have to store the TCP stream data by themselves again. After optimizing this procedure,the performance of stream reassembly module has been improved explicitly.
And further more,noff uses TCMalloc to optimize the memory allocation speed.
\subsection{Packets Filter}
Noff has afforded three kinds of filters.The first one is PF\_RING filter,you should use \textbf{pfring\_add\_filter\_rule} function to add a filter rule on an existing ring.
The second one is BPF\_filter. BPF supports filtering packets, allowing a userspace process to supply a filter program that specifies which packets it wants to receive.
The third one is protocol filter which is embedded in Ip fragment module.It can filter the packets in the callback interface.Now it can filter packets according to registered module and port.For instance,TCP modules can use \textbf{registerRule} function to specify which packets they don't need.In this way,some packets may not be sent to the upper layer module again.So filters can increase the system performance to a certain extent.
\newline\indent Noff also provide much statistical information.Noff not only provide the basic kernel dropping information but also provide the number of processed packets in each filter and each thread.All of this information would be indicated through the system log. The following code block exhibits part of system log which lists the number of packets handled by each thread.
\begin{lstlisting}[language=C]
20170528 08:44:57.964400Z 128795 INFO
worker1: 7754 - Dispatcher.cc:48
20170528 08:44:57.964403Z 128795 INFO
worker2: 16902 - Dispatcher.cc:48
20170528 08:44:57.964405Z 128795 INFO
worker3: 20434 - Dispatcher.cc:48
\end{lstlisting}
\indent Our implementation is based on an intel 520 XR2 NIC and a BCM5720 NIC.The XR2 is a modern 10GbE NIC supporting multiple queues and RSS while the BCM5720 is a 1000MbE NIC which only supports single receive queue.Noff can be effectively used with both these NICs. Actually according to our test,Noff can be executed on nearly all NICs platform.

\subsection{Callback Interface}
Noff use C++ bind/function feature to actualize callback interface.Bind scheme generates a forwarding call wrapper for a member function of a class.Calling this wrapper is equivalent to invoking a member function with some of its arguments bound to args. 
All module classes in noff should register their member function through this way.Once one function has been registered in a module.This module would store it into a vector.When a specific event happens,all call wrappers in the vector should be invoked one by one.This scheme is described vividly in Figure \ref{fig:6}.
\newline\indent Actually this scheme is similar to Observer Pattern.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.3\textwidth]{./picture/Figure5.jpg}
  \caption{callback interface scheme}
  \label{fig:6}
\end{figure}
\subsection{Packet Handle}
An application may be interested in receiving both reassembled streams, as well as their individual packets to detect TCP-level attacks.Different from traditional methods or to extract meritorious information from network traffic data. Because of callback interface in each module,noff's interfaces only offer necessary data for each module rather than delivering the original packets from the network.If an application indicates that it needs original data,in noff it needs to register with the capture module's interface.

@@

\subsubsection{Hardware}
In this paper,we use a testbed comprising two PCs interconnected directly through an Intel 520XR2 10GbE NIC and MT26448 10GbE NIC.Intel NIC is used as a stream capturer while MY26448 NIC is used for traffic generation. The two PCs are both equipped with one eight-core Intel Xeon 1.8GHz CPUs with 10MB L2 cache, 4GB RAM.Both PCs run 64-bit Ubuntu Linux(kernel version 4.4.50).
\subsubsection{Traffic}
To evaluate stream reassembly implementations with real traffic,we replay a traffic file which comes from campus network having totally two million TCP packets.
\subsubsection{Parameters}
We compare noff with the following libraries: (\uppercase\expandafter{\romannumeral1})Libnids v1.25\cite{Libnids}
(\uppercase\expandafter{\romannumeral2})and the Stream5 preprocessor of Snort v3.0.0. Libnids and Snort rely on Libpcap\cite{McCanne}, which uses the PF\_PACKET socket for packet capture on Linux while noff use PF\_PACKET directly .In our experiments, the size of this buffer is set to 512MB, and the buffer size for reassembled streams is set to 500000 for all of these three library.The other parameters for Libnids and Snort are all default.  
We set the keep-alive timer of noff as 60 seconds.As we replay the traffic data circularly,an inactivity timeout of 60 seconds is a reasonable choice.
\includegraphics[width=\textwidth]{./picture/Figure6.jpg}
\caption{Packet loss} 
\label{fig:7}
\includegraphics[width=\textwidth]{./picture/Figure7.jpg}
\caption{CPU Utilization}
\label{fig:8}

@@

\caption{Cpu utilization} 

@@

\subsection{Multiple Thread and Multiple Core}
In the Implementation section,we declare that the PF\_RING driver can support multiple queue NIC packet capture. In this experiment,we should verify the value of multiple thread.
\newline\indent Our 10GBE NIC can support 8 receive queues. So we would compare the performance of noff's TCP reassemble on single thread with the performance on multiple thread. Actually, multiple thread does not bring too much additional overhead.Each thread should burden the same procedure. Through NIC's RSS,each thread would only process one-eighth streams compared with the single thread scheme.
\newline\indent The Figure \ref{fig:11} and Figure \ref{fig:12} indicate the experiment result which include the performance of noff on two cases.From the result, we can clearly see that the single thread case starts to drop packets when the traffic rate exceeds 4Gbit/s while the multiple thread case drops no packet even the the traffic rate exceeds 6Gbit/s.We can find the reason from \ref{fig:11}.when the traffic rate exceeds 4Gbit/s,the single core utilization arrives the threshold(100\%) which means noff arrives its limitation on single core.But on multiple core platform,noff can use several cores to improve its processing ability.The utilization of it can exceed 100\%.This experiment prove that by multiple thread scheme,noff can obtain better performance extremely.
\begin{figure}
\begin{minipage}[t]{0.495\linewidth}
\flushleft
\includegraphics[width=\textwidth]{./picture/Figure10.jpg}
\caption{Cpu utilization} 
\label{fig:11}
\end{minipage}
\begin{minipage}[t]{0.495\linewidth}
\flushright
\includegraphics[width=\textwidth]{./picture/Figure11.jpg}
\caption{Http Packet Number}
\label{fig:12}
\end{minipage}
\end{figure} 
\newline\indent In the implementation section, we also refer an user-level multiple thread scheme.Different from the RSS method.The user-level method has an extra memory copy and brings a synchronization Lock.So the user-level multiple thread can not always improve performance.According to our experiment,when the work per thread is too heavy,the user-level multiple thread may become a better choice.

\subsection{TCMalloc Optimization}
Memory copy always bring remarkable influence to performance.In this paper we adopt the TCMalloc tool to accelerate the memory copy process.In this experiment, we 
would compare the noff's performance in the two cases:with TCMalloc and without TCMalloc.In order to control the variables,we decide to reuse the test scenario in TCP stream reassembly experiment.
\newline\indent The Figure \ref{fig:13} and Figure \ref{fig:14} indicate the result of experiment.From the Figure \ref{fig:13},we can see that the CPU utilization is slightly higher when we don't use TCMalloc. So the consequence is that when we don't use TCMalloc noff starts to drop packets when the network traffic exceeds 3.5Gbit/s.This check experiment prove that TCMalloc can improve the memory copy performance to a certain extent.
\newline\indent The full name of TCMalloc is thread cache malloc. One of the key  exploring spots is the thread local cache. In multiple thread environment,noff's module classes are all thread cache variables. So In this environment,the TCMalloc tool is a much better memory allocation optimization method.
\begin{figure}
\begin{minipage}[t]{0.495\linewidth}
\flushleft
\includegraphics[width=\textwidth]{./picture/Figure12.jpg}
\caption{Packet loss} 
\label{fig:13}
\end{minipage}
\begin{minipage}[t]{0.495\linewidth}
\flushright
\includegraphics[width=\textwidth]{./picture/Figure13.jpg}
\caption{Cpu utilization}
\label{fig:14}
\end{minipage}
\end{figure}

\subsection{Concurrent Traffic}
In the previous section,we have involved the Least Recently Used algorithm implementation and timing wheel scheme to manage the stream hash table.In this experiment, we need to confirm the effectiveness of these two methods.In order to attain the objective, we hope to verify this system from two aspects: multiple concurrent traffic processing and the no FIN streams processing.
\newline\indent For the first aspects,we use a real network TCP traffic set from SJTU campus network as the test data.In this set,there are totally about 50000 streams.We would vary the size of stream hash table of noff and libnids from 500 to 30000.Then record the number of loss streams of libnids and noff.
The figure \ref{fig:15} indicates the result of experiment.From the figure,we can explicitly see that libnids drops more streams than noff under the same circumstances. Actually these two library would eventually drop about 4000 streams when they have plenitudinous table size. 
\newline\indent For the second aspects,we have imitated multiple streams. These streams are all no FIN packets.In this way, if the capture library has no scheme to erase the dead streams.The streams would take up one position of 
the table.Noff can use time wheel to kick away the dead streams.So it should have a better performance in this situation.The figure \ref{fig:16} indicates the result of this experiment.we imitate the no FIN stream at the speed of 10Mbit/s and compare the number of loss stream of noff and libnids from 10s to 
120s.From the figure \ref{fig:16} we can see that noff and libnids have similar performance before 60s while noff obviously drop less packets after 60s for that noff's keep-alive timer works.The timer drops the dead stream from stream table.
\newline\indent Through these two experiments,we can reach the conclusion that noff has a better stream manager scheme.It can process multiple streams more flexibility.
\begin{figure}
\begin{minipage}[t]{0.49\linewidth}
\flushleft
\includegraphics[width=\textwidth]{./picture/Figure14.jpg}
\caption{Packet loss} 
\label{fig:15}
\end{minipage}
\begin{minipage}[t]{0.49\linewidth}
\flushright
\includegraphics[width=\textwidth]{./picture/Figure15.jpg}
\caption{CPU utilization}
\label{fig:16}
\end{minipage}
\end{figure}

@@

\subsection{Kernel Capture Optimization}
Scap is a novel capture library whose most attractive distinguishing characteristic is that it offer a NIC driver to process packet data in multiple receive queue.Its modules are mainly deployed in kernel level which means it has an aggressive performance.And scap also provide some  meticulous system optimization method.To tell the truth,scap is actually an excellent research work. By contrast, noff directly use PF\_RING driver to accomplish the similar function.But noff also support an user-level multiple thread platform to enhancing the versatility of the library.After all,not all NIC support multiple receive queue.

\subsection{Multicore Architecture}
Multicore architecture creates a new epoch in research on parallel processing.Many researches have been done.For example Low-level CPU optimizations like those of
L2-cache is one practical solution for fast parallelization\cite{Zhanikeev} and Chen et al. \cite{MapReduce} perform parallel processing of Big Data but optimize resource use.Marat Zhanikeev\cite{Zhanikeev} proposed a lockfree method to speed up capture process.Scap\cite{Papadogiannakis} is another kernel-level based optimization method.Noff adopt a lockfree user-level multi-thread platform.
\subsection{TCP Stream Reassembly}
Libnids\cite{Libnids} and Stream5\cite{Sturges} perform TCP reassembly based on the emulation of a network stack. Noff propose a more high-performance reassembly engine which optimize the drawbacks of libnids.

\subsection{Structure Optimization}
Luca Deri\cite{Deri} proposed a method based on polling frame to optimize the packets processing procedure.Yeim-Kuan\cite{Chang} make use of hierarchical binary prefix search scheme to process packets.Noff uses flexible callback interface to help programmers to build flexible structure easily.

\section{Conclusion}
In this paper,we have analyzed the difficulty in capturing and parsing the completed traffic network stream. So a high-Performance capture traffic is badly demanded.Actually 
most programmers not only need a high-Performance capture but also need a flexible extendible library to add aggressive applications.To cope with this conundrum. We have proposed our work:noff which is a flexible high-performance network traffic capture library.It has both kernel-level and user-level based multi-thread scheme to adapt to nearly all kinds of NICs.And it offers many flexible callback interfaces to help programmers to organise the system framework effectively.Compared with existing library libnids, noff has Imposed a variety of optimization such as memory allocation,TCP reassembly and so on.In this paper we evaluate our implementation through several experiments.
\newline\indent The results of our experimental evaluation demonstrate that noff can  capture network traffic for speed up to 4Gbit/s without packets loss using a single core which is better than the other existing approaches.A HTTP parsing application based on noff's platform is also performed better than the the other existing approaches.Moreover,noff support multi-thread,using this scheme noff can cope with the network traffic whose speed is up to 6Gbit/s easily.Meanwhile,noff's stream management algorithm help it to drop nearly 50\% fewer streams than the existing approaches when facing the high concurrence traffic.We can also build a new application based on noff faster.
\newline\indent We believe our implementation can bring some novel idea for developing an
attractive network library.

@@

We would like to thank the junior student GuangQian Peng.He has offered huge contribution to this research work.This research was performed with the financial support from a industrial project. The experts of SJTU also have involved in this project and offered some valuable feedback.

@@

@@

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Nowadays,the deep packet inspection(DPI) becomes a crucial technique to monitor the security of network which needs the completed information of network traffic packets.This technique claim an extremely strict requirement on the functionality and performance of a monitor subsystem.Therefore, a high-performance easy-use network traffic capture library is extremely required to help to build some attractive DPI applications.
\newline\indent To feed this demand,this paper proposes a flexible parallel network library(noff) which has ability to process the network traffic in multiple Gbps speed.With several innovative software techniques,noff has remarkably optimized the packets delivery procedure and the streams reassembly procedure compared with some traditional methods.Supporting two
kinds of parallel processing on multi-core architectures, minimizing memory allocation and dropping silent streams effectively are the main features of noff.Some well-designed experimental evaluations indicate that noff can perform better than other software libraries in streams reassembly and http parser on single core, and can process much higher traffic loads when using multi-core platform.

\end{abstract}

@@

The zero-copy and multi-core technology can help avoid sparse sampling\cite{Ali}.A renowned tool to accomplish zero-copy is PF\_RING\cite{PFRING}\cite{Luca}.The PF\_RING kernel module runs as a software interrupt handler that stores incoming packets to a memory-mapped buffer,shared with user-level stub.For multi-core technology,there are also various multi-thread proposed methods that can improve the entire performance.

@@

\subsection{PF\_RING Patch}
PF\_RING is a new type of network socket that can dramatically improve the packet capture speed.It uses User-space ZC (new generation DNA, Direct NIC Access) drivers for extreme packet capture transmission speed as the NIC NPU (Network Process Unit) is pushing getting packets to user land without any kernel intervention. 
Noff uses PF\_RING as the kernel driver and can thus arrive more aggressive runtime speed.

\subsection{LRU Scheme}
Noff has proposed Least Recently Used(LRU):a stream algorithm which enables the system to control its resources effectively during overload. This algorithm can resolve the problem that sudden traffic bursts or overload conditions may force the packet capturing subsystem to fill up its buffers and randomly drop streams in a haphazard manner.In order to arrive this requirment,noff maintains a novel timer data structure:timing wheel\cite{Varghese}which store the streams into different buckets by the time gap.Timing wheel would drop the streams which have been silent for at least one minute.In this way,the new stream will be accommodated with a higher probability.Besides,Programmers can also force to maintain some priority streams by updating the timestamp of those streams.The detail implementation of timing wheel would be described in the implementation section.

@@

\subsection{Processing Procedure}
Noff uses a multi-layer framework. Each layer is independent and could include a number of modules.A module would offer one or more callback interface for upper layer module to invoke. A stream packet's processing procedure is shown as Figure \ref{fig:3}.
Programmer can add a new module based on one existing layer by themselves.
\begin{figure}
\begin{minipage}[t]{0.495\linewidth}
\flushleft
\includegraphics[width=\textwidth]{./picture/Figure1.jpg}
\caption{Multiple Queues Capture} 
\label{fig:1}
\end{minipage}
\begin{minipage}[t]{0.495\linewidth}
\flushright
\includegraphics[width=\textwidth]{./picture/Figure2.jpg}
\caption{Single Queue Capture}
\label{fig:2}
\end{minipage}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{./picture/Figure3.jpg}
  \caption{Packet Processing Procedure}
  \label{fig:3}
\end{figure}

@@

    dns.addResponsecallback(bind(
    &UdpClient::onData<DnsResponse>,
    dnsResponseOutput.get(), _1));
}
void initInThread()
{
 setDnsCounterInThread();
}
\end{lstlisting}
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.25\textwidth]{./picture/Figure4.jpg}
  \caption{An Example of The Module}
  \label{fig:4}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.25\textwidth]{./picture/Figure16.jpg}
  \caption{Schematic Diagram of Timing Wheel}
  \label{fig:5}
\end{figure}
\subsubsection{Memory Optimization}
The TCP reassembly module needs to resort TCP fragments.So it needs to prestore packet data which is meant by a large number of dynamic memory allocation. Libnids not only prestore packets but also store the completed packets between client and server. This scheme has a palpable short slab that there are too many memory allocations and copies which could bring huge overhead.
\newline\indent Basically, noff has abandon the scheme that the reassembly module needs to store the completed packets. Because though libnids offer this ability. The upper applications also have to store the TCP stream data by themselves again. After optimizing this procedure,the performance of stream reassembly module has been improved explicitly.
And further more,noff uses TCMalloc to optimize the memory allocation speed.
\subsection{Packets Filter and Statistic}
Noff has afforded three kinds of filters.The first one is PF\_RING filter,you should use \textbf{pfring\_add\_filter\_rule} function to add a filter rule on an existing ring.
The second one is BPF\_filter. BPF supports filtering packets, allowing a userspace process to supply a filter program that specifies which packets it wants to receive.
The third one is protocol filter which is embedded in Ip fragment module.It can filter the packets in the callback interface.Now it can filter packets according to registered module and port.For instance,TCP modules can use \textbf{registerRule} function to specify which packets they don't need.In this way,some packets may not be sent to the upper layer module again.So filters can increase the system performance to a certain extent.
\newline\indent Noff also provides much statistical information.Noff provides not only the basic kernel dropping information but also the number of processed packets in each filter and each thread.All of this information would be indicated through the system log. The following code block exhibits part of system log which lists the number of packets handled by each thread.
\begin{lstlisting}[language=C]
20170528 08:44:57.964400Z 128795 INFO
worker1: 7754 - Dispatcher.cc:48
20170528 08:44:57.964403Z 128795 INFO
worker2: 16902 - Dispatcher.cc:48
20170528 08:44:57.964405Z 128795 INFO
worker3: 20434 - Dispatcher.cc:48
\end{lstlisting}
\indent Our implementation is based on an intel 520 XR2 NIC and a BCM5720 NIC.The XR2 is a modern 10GbE NIC supporting multiple queues and RSS while the BCM5720 is a 1000MbE NIC which only supports single receive queue.Noff can be effectively used with both these NICs. Actually according to our test,Noff can be executed on nearly all NICs platform.

\subsection{Callback Interface}
Noff use C++ bind/function feature to actualize callback interface.Bind scheme generates a forwarding call wrapper for a member function of a class.Calling this wrapper is equivalent to invoking a member function with some of its arguments bound to args. 
All module classes in noff should register their member function through this way.Once one function has been registered in a module.This module would store it into a vector.When a specific event happens,all call wrappers in the vector should be invoked one by one.This scheme is described vividly in Figure \ref{fig:6}.
\newline\indent Actually this scheme is similar to Observer Pattern.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.3\textwidth]{./picture/Figure5.jpg}
  \caption{Callback Interface Scheme}
  \label{fig:6}
\end{figure}
\subsection{Packet Handle}
An application may be interested in receiving both reassembled streams, as well as their individual packets to detect TCP-level attacks.Different from traditional methods or to extract meritorious information from network traffic data. Because of callback interface in each module,noff's interfaces only offer necessary data for each module rather than delivering the original packets from the network.If an application indicates that it needs original data,in noff it needs to register with the capture module's interface.

@@

\subsubsection{Hardware}
In this paper,we use a testbed comprising two PCs interconnected directly through an Intel 520XR2 10GbE NIC and MT26448 10GbE NIC.Intel NIC is used as a stream capturer while MY26448 NIC is used for traffic generation. The two PCs are both equipped with one eight-core Intel Xeon 1.8GHz CPUs with 10MB L2 cache, 4GB RAM.Both PCs run 64-bit Ubuntu Linux(kernel version 4.4.50).
\begin{figure}
\begin{minipage}[t]{0.495\linewidth}
\flushleft
\includegraphics[width=\textwidth]{./picture/Figure6.jpg}
\caption{Packet loss} 
\label{fig:7}
\end{minipage}
\begin{minipage}[t]{0.495\linewidth}
\flushright
\includegraphics[width=\textwidth]{./picture/Figure7.jpg}
\caption{CPU Utilization}
\label{fig:8}
\end{minipage}
\end{figure} 
\subsubsection{Traffic}
To evaluate stream reassembly implementations with real traffic,we replay a traffic file which comes from campus network having totally two million TCP packets.
\subsubsection{Parameters}
We compare noff with the following libraries: (\uppercase\expandafter{\romannumeral1})Libnids v1.25\cite{Libnids}
(\uppercase\expandafter{\romannumeral2})and the Stream5 preprocessor of Snort v3.0.0. Libnids and Snort rely on Libpcap\cite{McCanne}, which uses the PF\_PACKET socket for packet capture on Linux while noff use PF\_PACKET directly .In our experiments, the size of this buffer is set to 512MB, and the buffer size for reassembled streams is set to 500000 for all of these three library.The other parameters for Libnids and Snort are all default.  
We set the keep-alive timer of noff as 60 seconds.As we replay the traffic data circularly,an inactivity timeout of 60 seconds is a reasonable choice.

@@

\caption{CPU Utilization of HTTP Parser} 

@@

\includegraphics[width=\textwidth]{./picture/Figure10.jpg}
\caption{CPU Utilization of Single and Multiple Thread} 
\label{fig:11}
\includegraphics[width=\textwidth]{./picture/Figure11.jpg}
\caption{Packet Loss of Single and Multiple Thread}
\label{fig:12}
\subsection{Multiple Thread and Multiple Core}
In the Implementation section,we declare that the PF\_RING driver can support multiple queue NIC packet capture. In this experiment,we should verify the value of multiple thread.
\newline\indent Our 10GBE NIC can support 8 receive queues. So we would compare the performance of noff's TCP reassemble on single thread with the performance on multiple thread. Actually, multiple thread does not bring too much additional overhead.Each thread should burden the same procedure. Through NIC's RSS,each thread would only process one-eighth streams compared with the single thread scheme.
\newline\indent The Figure \ref{fig:11} and Figure \ref{fig:12} indicate the experiment result which include the performance of noff on two cases.From the result, we can clearly see that the single thread case starts to drop packets when the traffic rate exceeds 4Gbit/s while the multiple thread case drops no packet even the the traffic rate exceeds 6Gbit/s.We can find the reason from \ref{fig:11}.when the traffic rate exceeds 4Gbit/s,the single core utilization arrives the threshold(100\%) which means noff arrives its limitation on single core.But on multiple core platform,noff can use several cores to improve its processing ability.The utilization of it can exceed 100\%.This experiment prove that by multiple thread scheme,noff can obtain better performance extremely.
\newline\indent In the implementation section, we also refer an user-level multiple thread scheme.Different from the RSS method.The user-level method has an extra memory copy and brings a synchronization Lock.So the user-level multiple thread can not always improve performance.According to our experiment,when the work per thread is too heavy,the user-level multiple thread may become a better choice.

\subsection{TCMalloc Optimization}
Memory copy always bring remarkable influence to performance.In this paper we adopt the TCMalloc tool to accelerate the memory copy process.In this experiment, we 
would compare the noff's performance in the two cases:with TCMalloc and without TCMalloc.In order to control the variables,we decide to reuse the test scenario in TCP stream reassembly experiment.
\newline\indent The Figure \ref{fig:13} and Figure \ref{fig:14} indicate the result of experiment.From the Figure \ref{fig:13},we can see that the CPU utilization is slightly higher when we don't use TCMalloc. So the consequence is that when we don't use TCMalloc noff starts to drop packets when the network traffic exceeds 3.5Gbit/s.This check experiment prove that TCMalloc can improve the memory copy performance to a certain extent.
\newline\indent The full name of TCMalloc is thread cache malloc. One of the key  exploring spots is the thread local cache. In multiple thread environment,noff's module classes are all thread cache variables. So In this environment,the TCMalloc tool is a much better memory allocation optimization method.
\begin{figure}
\begin{minipage}[t]{0.495\linewidth}
\flushleft
\includegraphics[width=\textwidth]{./picture/Figure12.jpg}
\caption{CPU Utilization with TCMalloc or not} 
\label{fig:13}
\end{minipage}
\begin{minipage}[t]{0.495\linewidth}
\flushright
\includegraphics[width=\textwidth]{./picture/Figure13.jpg}
\caption{Packet Loss with TCMalloc or not}
\label{fig:14}
\end{minipage}
\end{figure}

\subsection{Concurrent Traffic}
In the previous section,we have involved the Least Recently Used algorithm implementation and timing wheel scheme to manage the stream hash table.In this experiment, we need to confirm the effectiveness of these two methods.In order to attain the objective, we hope to verify this system from two aspects: multiple concurrent traffic processing and the no FIN streams processing.
\newline\indent For the first aspects,we use a real network TCP traffic set from SJTU campus network as the test data.In this set,there are totally about 50000 streams.We would vary the size of stream hash table of noff and libnids from 500 to 30000.Then record the number of loss streams of libnids and noff.
The figure \ref{fig:15} indicates the result of experiment.From the figure,we can explicitly see that libnids drops more streams than noff under the same circumstances. Actually these two library would eventually drop about 4000 streams when they have plenitudinous table size. 
\newline\indent For the second aspects,we have imitated multiple streams. These streams are all no FIN packets.In this way, if the capture library has no scheme to erase the dead streams.The streams would take up one position of 
the table.Noff can use time wheel to kick away the dead streams.So it should have a better performance in this situation.The figure \ref{fig:16} indicates the result of this experiment.we imitate the no FIN stream at the speed of 10Mbit/s and compare the number of loss stream of noff and libnids from 10s to 
120s.From the figure \ref{fig:16} we can see that noff and libnids have similar performance before 60s while noff obviously drop less packets after 60s for that noff's keep-alive timer works.The timer drops the dead stream from stream table.
\newline\indent Through these two experiments,we can reach the conclusion that noff has a better stream manager scheme.It can process multiple streams more flexibility.
\begin{figure}
\begin{minipage}[t]{0.49\linewidth}
\flushleft
\includegraphics[width=\textwidth]{./picture/Figure14.jpg}
\caption{Stream Loss with Different Hash Table Size} 
\label{fig:15}
\end{minipage}
\begin{minipage}[t]{0.49\linewidth}
\flushright
\includegraphics[width=\textwidth]{./picture/Figure15.jpg}
\caption{Stream Loss with Different Duration}
\label{fig:16}
\end{minipage}
\end{figure}

@@

\subsection{Kernel Capture Optimization}
Scap\cite{Papadogiannakis} is a novel capture library whose most attractive distinguishing characteristic is that it offer a NIC driver to process packet data in multiple receive queue.Its modules are mainly deployed in kernel level which means it has an aggressive performance.And scap also provide some  meticulous system optimization method.To tell the truth,scap is actually an excellent research work. By contrast, noff directly use PF\_RING driver to accomplish the similar function.But noff also support an user-level multiple thread platform to enhancing the versatility of the library.After all,not all NIC support multiple receive queue.

\subsection{Multicore Architecture}
Multicore architecture creates a new epoch in research on parallel processing.Many researches have been done.For example Low-level CPU optimizations like those of
L2-cache is one practical solution for fast parallelization\cite{Zhanikeev} and Chen et al. \cite{MapReduce} perform parallel processing of Big Data but optimize resource use.Marat Zhanikeev\cite{Zhanikeev} proposed a lockfree method to speed up capture process.Scap\cite{Papadogiannakis} is another kernel-level based optimization method and Schultz\cite{Schultz} claims that baremetal can handle the 10Gbps traffic on a single core.Noff adopt a lockfree user-level multi-thread platform.
\subsection{TCP Stream Reassembly}
Libnids\cite{Libnids} and Stream5\cite{Sturges} perform TCP reassembly based on the emulation of a network stack. Noff propose a more high-performance reassembly engine which optimize the drawbacks of libnids.

\subsection{Structure Optimization}
Luca Deri\cite{Deri} proposed a method based on polling frame to optimize the packets processing procedure.Yeim-Kuan\cite{Chang} make use of hierarchical binary prefix search scheme to process packets.Noff uses flexible callback interfaces to help programmers to build flexible structure easily.

\section{Conclusion}
In this paper,we have analyzed the significance in capturing and parsing the completed traffic network stream. So a high-performance capture traffic is badly demanded.Actually most programmers need a high-Performance capture as well as a flexible extendible library to add some aggressive applications.To cope with this conundrum. We have proposed our work:noff which is a flexible high-performance network traffic capture library.It has both kernel-level and user-level based multi-thread scheme to adapt to nearly all kinds of NICs.And it offers many flexible callback interfaces to help programmers to organise the system framework effectively.Compared with existing library libnids, noff has Imposed a variety of optimization such as memory allocation,TCP reassembly and so on.In this paper we evaluate our implementation through several experiments.
\newline\indent The results of our experimental evaluation demonstrate that noff can  capture network traffic for speed up to 4Gbit/s without packets loss using a single core which is better than the other existing approaches.A HTTP parsing application based on noff's platform is also performed better than the the other existing approaches.Moreover,noff support multi-thread,using this scheme noff can cope with the network traffic whose speed is up to 6Gbit/s easily.Meanwhile,noff's stream management algorithm help it to drop nearly 50\% fewer streams than the existing approaches when facing the high concurrence traffic.We can also build a new application based on noff faster.
\newline\indent We believe our implementation can bring some novel idea for developing an
attractive network library.

@@

We would like to thank the junior student Guangqian Peng.He has offered a huge contribution to this research work.This research was performed with the financial support from an industrial project. The experts of SJTU also have been involved in this project and offered some valuable feedback.

@@

  \bibitem{Luca}
  Luca Deri, “Modern Packet Capture and Analysis: Multi-Core, Multi-
Gigabit, and Beyond”, Internet Measurement (IM) Tutorial, 2009.

@@

  \bibitem{Schultz}
  Schultz, Michael J., and P. Crowley. "Performance Analysis of Packet Capture Methods in a 10 Gbps Virtualized Environment." International Conference on Computer Communications and Networks IEEE, 2012:1-8.
